Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-29 article.tex
small modifs from DE

This appendix is structured as follows: Section~\ref{sapp:signal} describes the
differences in terms of signal processing. Section~\ref{sapp:averaging} then
provides a detailed presentation of the averaging
approach. Section~\ref{sapp:connectome} presents a heuristic to retrieve edge
directionality. Finally, Section~\ref{sapp:results} presents some experimental
results to validate the different steps of our proposal.

@@

This approach is based on the following
observation. The rise of fluorescence of a neuron indicates its
activation. If another neuron is activated after a slight delay, this
could be a consequence of the activation of the first neuron and
therefore indicates a directed link in the connectome from the first to
the second neuron.  Given this observation, we have computed for every
pair $(i,j)$ an empirical estimation of the  term:
\begin{align}
s_{i,j} = \sum_x \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
\end{align}
that could be interpreted as an image of the  number of times
that neuron $i$ activates neuron $j$. $\phi_1$ and $\phi_2$ are
parameters whose values have been chosen in our experiments equal to   
$0.2$ and $0.5$, respectively. Their role is
define when the difference between $x_j^{t+1}$  and $x_i^t$ can
indeed be assimilated to an event where neuron $i$ activates neuron
$j$.

>>>>

This appendix is structured as follows: Section~\ref{sapp:signal} describes the
differences in terms of signal processing. Section~\ref{sapp:averaging} then
provides a detailed presentation of the averaging
approach. Section~\ref{sapp:connectome} presents an approach to retrieve edge
directionality. Finally, Section~\ref{sapp:results} presents some experimental
results to validate the different steps of our proposal.

@@

This approach is based on the following
observation. The rise of fluorescence of a neuron indicates its
activation. If another neuron is activated after a slight delay, this
could be a consequence of the activation of the first neuron and
therefore indicates a directed link in the connectome from the first to
the second neuron.  Given this observation, we have computed for every
pair $(i,j)$ an empirical estimation of the  term:
\begin{align}
s_{i,j} = \sum_x \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
\end{align}
that could be interpreted as an image of the  number of times
that neuron $i$ activates neuron $j$. $\phi_1$ and $\phi_2$ are
parameters whose values have been chosen in our experiments equal to   
$0.2$ and $0.5$, respectively. Their role is to 
define when the difference between $x_j^{t+1}$  and $x_i^t$ can
indeed be assimilated to an event where neuron $i$ activates neuron
$j$.
